Empirical Evaluation of eval in R

### 2020-08-26 inst/analysis/analysis_stable.Rmd
Reduce the number of unknown evals

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
        self_contained: no
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR

@@

eval_call_core <- 
  read_fst(packages_filepath) %>%
  as_tibble() %>%
  mutate(dataset = "core")

@@

@@

@@

We also look to the occurences of `paste` and `str_c` in the `parse` argument. It is an indication that meta-pogramming happens.

```{r parse_meta_prog}
meta_parsed <- parsed_texts %>% filter(str_detect(expr_parsed_expression, "paste|str_c"))

@@

>>>>

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR

@@

eval_call_core <- 
  read_fst(core_filepath) %>%
  as_tibble() %>%
  mutate(dataset = "core")

@@

```{r unique_calls}
nb_unique_calls <- nrow(eval_calls)

r("unique calls", nb_unique_calls)
```

There are `r nb_unique_calls` unique calls;

@@

### Unknown evals

Some `eval` do not have srcref information attached and are not in *base*. It is often because they are located in a function that is created by anotehr function.

```{r unknown_evals}
undefined_evals <- eval_calls %>% filter(eval_source_type == "<undefined>")

nb_undefined <- undefined_evals %>% count(wt = nb_ev_calls)

nb_different_call_expr <- undefined_evals %>% select(eval_call_expression) %>% n_distinct()

r("undefined evals", nb_undefined$n)
r("percent undefined eval", ratio(nb_undefined$n, nb_eval_calls))
r("undefined eval expressions", nb_different_call_expr)
```

@@

We also look to the occurrences of `paste` (and `parse0`), `glue` and `str_c` in the `parse` argument. It is an indication that meta-pogramming happens.

```{r parse_meta_prog}
meta_parsed <- parsed_texts %>% filter(str_detect(expr_parsed_expression, "paste|str_c|glue"))

@@

We can look at the most common meta-programming examples:

```{r parse_meta_prog_ex}
meta_parsed %>% count(expr_parsed_expression, wt = nb_ev_calls, sort = TRUE)
```
